\boldmath Primordial Black Hole Formation in a Dust Bouncing Model

### 2024-12-04 main.tex
Minor changes and sent to referee

	{
		\color{red} As a final remark, it is evident that, in the classical theory, one
		could interchangeably use either $\bar{H}^2$ or $\kappa \bar{\rho}/3$, as they are
		related by the classical Friedmann equation. However, in the quantum framework,
		$\bar{\rho}$ retains the same functional dependence on the scale factor, whereas
		$\bar{H}^2$ acquires an additional term due to quantum effects absent in the
		classical theory. Consequently, when deriving the Lagrangian for perturbations, it
		is crucial to avoid relying on the classical Friedmann equations. This approach was
		explicitly followed in Ref.~\cite{fluidgeral}, where the authors computed
		perturbations up to second order without invoking any classical background
		equations.

@@

{\color{red} Before we proceed, we must emphasize that we are considering the formation
of PBHs in a classical context. We are using the quantum fields to describe the initial
conditions of the perturbations, but the contracting phase is amplifying their
amplitudes in a similar fashion to an inflationary phase. Such assumptions, particularly
regarding the quantum-to-classical transition, are commonplace in the literature,
especially in inflationary models. For example, in Ref.~\cite{Q2C}, the authors discuss
the quantum-to-classical transition in the context of the Bohmian-De Broglie
interpretation, showing that the quantum potential is negligible when the perturbations
are amplified by the inflationary phase.

>>>>

	{
		\color{red} As a final remark, it is evident that, in the classical theory, one
		could interchangeably use either $\bar{H}^2$ or $\kappa \bar{\rho}/3$, as they are
		related by the classical Friedmann equation. However, in the quantum framework,
		$\bar{\rho}$ retains the same functional dependence on the scale factor, whereas
		$\bar{H}^2$ acquires an additional term due to quantum effects absent in the
		classical theory. Consequently, when deriving the Lagrangian for perturbations, it
		is crucial to avoid relying on the classical Friedmann equations. This approach was
		explicitly followed in Ref.~\cite{fluidgeral}, where the authors computed
		perturbations up to the second order without invoking any classical background
		equations.

@@

{\color{red} Before we proceed, we must emphasize that we are considering the formation
of PBHs in a classical context. We are using the quantum fields to describe the initial
conditions of the perturbations, but the contracting phase is amplifying their
amplitudes in a similar fashion to an inflationary phase. Such assumptions, particularly
regarding the quantum-to-classical transition, are commonplace in the literature,
especially in inflationary models. For example, in Ref.~\cite{Q2C2}, the authors discuss
the quantum-to-classical transition in the context of the Bohmian-De Broglie
interpretation, showing that the quantum potential is negligible when the perturbations
are amplified by the inflationary phase.
